Every Author as First Author

### 2023-03-27 paper.tex
Amusing author orders and BST improvements

Authorship order makes for fraught debates in academia.
Perhaps the most common standard is to list authors in reverse order by
significance of contributions to the work.
But this quantity is usually difficult to measure,
and can lead to uncomfortable conversations, arguments, or even feuds.
For example, are an advisor's leadership and high-level ideas
more or less important than a student's technical solutions?
Is one author's technical work more or less important than
another author's writing of the paper?
Even if the answer to these questions are clear to you
(and equal among all authors), authors' contributions are rarely so clearcut.
And what if the contributions are roughly equal?

@@

>>>>

Authorship order makes for fraught debates in academia.
Perhaps the most common standard is to list authors in decreasing order
by significance of contributions to the work.
But this quantity is usually difficult to measure,
and can lead to uncomfortable conversations, arguments, or even feuds.
For example, are an advisor's leadership and high-level ideas
more or less important than a student's technical solutions?
Is one author's technical work more or less important than
another author's writing of the paper?
Even if the answer to these questions are clear to you
(and equal among all authors), authors' contributions are rarely so clearcut.
And what if the contributions are roughly equal?

@@

To compensate for alphabetical discrimination,
several specific papers have explored alternate strategies
to automatic authorship order than alphabetical,
and report the strategy in a footnote.
These strategies include competition via
25-game croquet series \cite{croquet},
2-day backgammon contest \cite{backgammon},
tennis match \cite{tennis},
basketball free throws \cite{free-throws},
arm wrestling \cite{arm-wrestling},
brownie bake-off \cite{brownie-bakeoff},
a game of chicken \cite{chicken},
rock paper scissors \cite{rock-paper-scissors},
coin toss \cite{coin-toss},
dice roll \cite{dice},
the outcome of famous cricket games \cite{cricket},
currency exchange rate fluctuation \cite{currency-fluctuation},
dog treat consumption order \cite{dog},
author height \cite{height},
fertility \cite{fertility},
proximity to tenure \cite{tenure-proximity},
reverse alphabetical order \cite{reverse-alphabetical},
and degree of belief in the paper's thesis \cite{belief}.
Others have proposed games such as Russian roulette
(``publish and perish'') \cite{publish-and-perish}.
See the excellent surveys \cite{survey1,survey2,survey3}
and their comments.
